---
title: "8-Factors Model by Machine Learning"
author: "Ma Yadong"
date: "2017/4/17"
output: 
  beamer_presentation: 
    colortheme: rose
    fig_height: 6
    theme: CambridgeUS
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Intraduction

## Predict alpha returns with Machine Learning

- Traditional factor models are useful in portfolio selection
- Predicting alpha returns are of importance in factor models.
- Machine learning may give a better solution for prediction.
- LinearRegression, LogisticRegression, RandomForest_Classfier, RandomForest_Regression, Adaboost_Classfier, Adaboost_Regression

## What are factor models
- CAPM
$$E(r_i) = \beta_{0} + \beta_{1}r_{m} +\varepsilon_{i}$$

- Fama-French 3 Factors
$$r_{i} = \beta_{0} + \beta_{1}r_{m} + \beta_{2}r_{HML} +\beta_{3}r_{SMB} + \varepsilon_{i}$$
- Multi-factor model
$$r_{i} = \sum \beta_{i}f_{i}+ \varepsilon_{i}$$



## Datasets
- The dataset are **daily data** in China stock market from **2009-01-01** to **2017-03-31**
- Trading strategy:
    1. At each trade times, select the best K stocks from the whole market according to **Scores**
    2. ST stocks and price limit stocks are not included in our targets
    3. Change the position monthly (20 trade days in fact)
    4. The weight of each stocks aresimplified as **equivalent weight**.
    5. At each trading, we use **the past 12 months** data to train our model and then to predict the scores.
- Scores:
    1. We are going to divide the stocks into **GOOD** and **BAD** two groups (with labels 1 and 0 correspondingly)
    2. We rank the return of future 20 days. We label the first 30% as 1 (GOOD), and last 30% as 0 (BAD)
    3. After the each prediction of our claffier, **the predicted probablity of fall into GOOD group will be the scores**.


## Factors
1. **TotalValue**: the total capital value of stocks
2. **Reversal_DongFang**: a revesal indicator offered by DongFang Security
3. **Seasonal_NetProfitGrowth_YOY**: Net profit growth rate seasonally
4. **Turnover_ols_TotalValue**: value neutral turnover rate
5. **PB_lf**: latest Price bookvalue ratio
6. **HeteroRsquare_FF_d20**: Fama-French regression $R^2$
7. **PreRet_M_IndusRet_Citic1_m1**: Industrial neutral 1M monmentum
8. **PreRet_M_IndusRet_Citic1_m3**: Industrial neutral 3M monmentum


# Single Factor Test Overview

## TotalValue
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'TotalValue'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`



## Reversal_DongFang
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Reversal_DongFang'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`



## Seasonal_NetProfitGrowth_YOY
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Seasonal_NetProfitGrowth_YOY'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


## Turnover_ols_TotalValue
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Turnover_ols_TotalValue'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


## PB_lf
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'PB_lf'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


## HeteroRsquare_FF_d20
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'HeteroRsquare_FF_d20'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


## PreRet_M_IndusRet_Citic1_m1
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'PreRet_M_IndusRet_Citic1_m1'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


## PreRet_M_IndusRet_Citic1_m3
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'PreRet_M_IndusRet_Citic1_m3'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`



## PreRet_M_IndusRet_Citic1_m3
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'PreRet_M_IndusRet_Citic1_m3'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`


# Machine Learning methods results

## LinearRegression_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'LinearRegression_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('LinearRegression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.



## LinearRegression_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'LinearRegression_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('LinearRegression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## LogisticRegression_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'LogisticRegression_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('LogisticRegression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## LogisticRegression_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'LogisticRegression_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('LogisticRegression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## RandomForest_100_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_100'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.



## RandomForest_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## RandomForest_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.



## RandomForest_300_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_300'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.



## RandomForest_Regression_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_Regression_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## RandomForest_Regression_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_Regression_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## RandomForest_Regression_300_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'RandomForest_Regression_300'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('RandomForest_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.




## Adaboost_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Adaboost_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('Adaboost_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## Adaboost_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Adaboost_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('Adaboost_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.



## Adaboost_Regression_150_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Adaboost_Regression_150'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('Adaboost_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## Adaboost_Regression_200_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Adaboost_Regression_200'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('Adaboost_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.


## Adaboost_Regression_300_EW
```{r,warning=FALSE,echo=FALSE,message=FALSE}
library(PerformanceAnalytics)
tradedate <- read.csv('Tradedate.csv',header = F,col.names = 'date',colClasses = 'Date')$date
model <- 'Adaboost_Regression_300'
df <- read.csv(paste(model,'.csv',sep=''))[,-1]
score <- read.csv('Adaboost_Regression_score.csv')
score <- round(mean(na.omit(score[,2]))*100,2)
rownames(df) <- tradedate
colnames(df) <- c('Long-Short','Hedge HS300','Hedge ZZ500')
df <- as.xts(df)['2009/2017']
LongShort <- apply.monthly(x = df[,1],FUN = function(x){prod(1+x)-1})
Hedge300 <- apply.monthly(x = df[,2],FUN = function(x){prod(1+x)-1})
Hedge500 <- apply.monthly(x = df[,3],FUN = function(x){prod(1+x)-1})
ret <- cbind(LongShort,Hedge500)
maxdrawdown <- maxDrawdown(Hedge500)
maxdrawdown <- round(maxdrawdown*100,2)
annualized_ret <- Return.annualized(Hedge500)
annualized_ret <- round(annualized_ret*100,2)
sharperatio <- SharpeRatio(Hedge500)*sqrt(12)
sharperatio <- sharperatio[1]
sharperatio <- round(sharperatio,3)
charts.PerformanceSummary(ret,main = model)

```

- Ret:`r annualized_ret`%,MaxDrawdown:`r maxdrawdown`%,Sharpe ratio:`r sharperatio`,Score:`r score`%.
